Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment

### 2022-11-18 R/model_fcs_markdown.Rmd
Update

```{r}
sites <- read_csv(here("data", "processed", "data_processed_sites.csv"),
                  col_names = TRUE, na = c("na", "NA", ""), col_types =
                    cols(
                      .default = "?",
                      plot = "f",
                      site = "f",
                      sand_ratio = "f",
                      substrate_depth = col_factor(levels = c("30", "15")),
                      target_type = col_factor(levels = c(
                        "hay_meadow", "dry_grassland"
                      )),
                      seed_density = "f",
                      exposition = col_factor(levels = c(
                        "north", "south"
                      )),
                      survey_year = "c"
                    )) %>%
  ### Exclude data of seed mixtures
  filter(survey_year != "seeded") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    botanist_year = factor(botanist_year),
    n = fcs_target,
    id = factor(id)
    ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, botanist_year, n
    )
```

>>>>

```{r}
sites <- read_csv(
  here("data", "processed", "data_processed_sites.csv"),
  col_names = TRUE, na = c("na", "NA", ""), col_types =
    cols(
      .default = "?",
      plot = "f",
      site = "f",
      sand_ratio = "f",
      substrate_depth = col_factor(levels = c("30", "15")),
      target_type = col_factor(levels = c(
        "hay_meadow", "dry_grassland"
        )),
      seed_density = "f",
      exposition = col_factor(levels = c("north", "south")),
      survey_year = "c"
      )
  ) %>%
  ### Exclude data of seed mixtures
  filter(survey_year != "seeded") %>%
  mutate(
    survey_year_fct = factor(survey_year),
    botanist_year = str_c(survey_year, botanist, sep = " "),
    botanist_year = factor(botanist_year),
    n = fcs_target,
    id = factor(id)
    ) %>%
  select(
    id, plot, site, exposition, sand_ratio, substrate_depth, target_type,
    seed_density, survey_year_fct, survey_year, botanist_year, n
    )
```
